Sound Synthesis

### 2020-10-21 Text/04_LMS.tex
added LMS chapter

\subsection{Least Mean Squares}
The linear least mean squares, also known as linear regression \parencite{2018StephenBoydIntroduction} is a data fitting technique. % TODO

@@

In the constrained version of the least squares problem we are still interested in finding the coefficient vector $ \hat{A} $ that minimizes $ ||Q A - Y||^2_2 $, but respecting a restriction on this vector of the general form of $ V A = B $.

>>>>

\subsection{Least Mean Squares}

\newacronym{LMS}{LMS}{Least Mean Squares}

The linear \gls{LMS}, also known as linear regression \parencite{2018StephenBoydIntroduction} is a data fitting technique. % TODO

@@

\newacronym{CLMS}{CLMS}{Constrained Least Mean Squares}

In the constrained version of the \gls{LMS}, known as the \gls{CLMS} problem we are still interested in finding the coefficient vector $ \hat{A} $ that minimizes $ ||Q A - Y||^2_2 $, but respecting a restriction on this vector of the general form of $ V A = B $.
